How to select predictive models for decision-making or causal inference?

### 2024-06-02 how_to_select.tex
rm zone_identifier figures

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.8\linewidth]{caussim_example_rs_gaussian=8_rs_rotation=8_ntv=0.37_D=2_overlap=0.7_p_A=0.1.pdf}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \centering
        \caption{\textbf{Caussim}}
        \includegraphics[width=\textwidth]{normalized_bias_tau_risk_to_best_method_caussim__nuisance_non_linear__candidates_ridge__overlap_01-247.pdf}
        \label{fig:normalized_bias_tau_risk_to_best_method_caussim}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.44\textwidth}
        \centering
        \caption{\textbf{ACIC 2016}}
        \includegraphics[width=\textwidth]{normalized_bias_tau_risk_to_best_method_acic_2016__nuisance_non_linear__candidates_hist_gradient_boosting__dgp_1-77__rs_1-10.pdf}
        \label{fig:normalized_bias_tau_risk_to_best_method_acic_2016}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.10\textwidth}
        \centering
        \includegraphics[width=1.5\textwidth]{legend_metrics.pdf}
    \end{subfigure}
    \begin{subfigure}[b]{0.44\textwidth}
        \centering
        \caption{\textbf{ACIC 2018}}
        \includegraphics[width=\textwidth]{normalized_bias_tau_risk_to_best_method_acic_2018__nuisance_stacking__candidates_hist_gradient_boosting__tset_50.pdf}
        \label{fig:normalized_bias_tau_risk_to_best_method_acic_2018}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.44\textwidth}
        \centering
        \caption{\textbf{TWINS}}
        \includegraphics[width=\textwidth]{normalized_bias_tau_risk_to_best_method_twins__nuisance_stacking__candidates_hist_gradient_boosting__tset_50__overlap_11-296__rs_0-9_noise10.pdf}
        \label{fig:normalized_bias_tau_risk_to_best_method_twins}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.10\textwidth}
        ~
    \end{subfigure}
    \caption{Metric performances by normalized tau-risk distance to the best
        method selected with $\tau\text{-risk}$. All nuisances are learned with the
        same estimator stacking gradient boosting and ridge regression. Doted and
        plain lines corresponds to 60\% lowess quantile estimates. This choice of
        quantile allows to see better the oracle metrics lines for which outliers with a value
        of 0 distord the curves.}
    \label
    {apd:all_datasets_normalized_bias_tau_risk_to_best_method}
\end{figure}

>>>>

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.8\linewidth]{caussim_example.pdf}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \centering
        \caption{\textbf{Caussim}}
        \includegraphics[width=\textwidth]{normalized_bias_tau_risk_to_best_method_caussim__nuisance_non_linear__candidates_ridge__overlap_01-247.pdf}
        \label{fig:normalized_bias_tau_risk_to_best_method_caussim}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.44\textwidth}
        \centering
        \caption{\textbf{ACIC 2016}}
        \includegraphics[width=\textwidth]{normalized_bias_tau_risk_to_best_method_acic_2016__nuisance_non_linear__candidates_hist_gradient_boosting__dgp_1-77__rs_1-10.pdf}
        \label{fig:normalized_bias_tau_risk_to_best_method_acic_2016}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.10\textwidth}
        \centering
        \includegraphics[width=1.5\textwidth]{legend_metrics.pdf}
    \end{subfigure}
    \begin{subfigure}[b]{0.44\textwidth}
        \centering
        \caption{\textbf{ACIC 2018}}
        \includegraphics[width=\textwidth]{normalized_bias_tau_risk_to_best_method_acic_2018__nuisance_stacking__candidates_hist_gradient_boosting__tset_50.pdf}
        \label{fig:normalized_bias_tau_risk_to_best_method_acic_2018}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.44\textwidth}
        \centering
        \caption{\textbf{TWINS}}
        \includegraphics[width=\textwidth]{normalized_bias_tau_risk_to_best_method_twins__nuisance_stacking__candidates_hgb.pdf}
        \label{fig:normalized_bias_tau_risk_to_best_method_twins}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.10\textwidth}
        ~
    \end{subfigure}
    \caption{Metric performances by normalized tau-risk distance to the best
        method selected with $\tau\text{-risk}$. All nuisances are learned with the
        same estimator stacking gradient boosting and ridge regression. Doted and
        plain lines corresponds to 60\% lowess quantile estimates. This choice of
        quantile allows to see better the oracle metrics lines for which outliers with a value
        of 0 distord the curves.}
    \label
    {apd:all_datasets_normalized_bias_tau_risk_to_best_method}
\end{figure}
